Abstractions for Type-Level Programming

### 2022-05-11 symposium.tex
Rephrase,"the type of those groups..."

The main difference between Scala's original |Regex| implementation and ours lies in the signature of |unapply|, which determines the nature of pattern matching extraction performed by that method.
In our implementation, we instantiate the type |P| to a tuple and use that type in the result type of |unapply| to tell the compiler that a successful matching consists of exactly $n$ capturing groups, where $n$ is the tuple's arity.
Furthermore, the type of those groups corresponds to the type of the tuple elements.
% TODO L196: "Furthermore, the type of those groups corresponds to the type of the tuple elements." This part is a bit hard to understand at a first reading, because only later on L236, the reader learns that matched values can only be of type String or Option String, and there's a singular/plural mismatch ("the type" is singular but applies to each of "those groups"). It might help to rephrase this sentence and already mention "String or Option String".
This allows us to enrich the results of Java's regex engine by wrapping nullable values into options.
Our implementation performs this wrapping via the |transform| method, which is our runtime processing component.
As a result, our implementation never returns null values and removes the null-checking burden from the user.

>>>>

The main difference between Scala's original |Regex| implementation and ours lies in the signature of |unapply|, which determines the nature of pattern matching extraction performed by that method.
In our implementation, we instantiate the type |P| to a tuple and use that type in the result type of |unapply| to tell the compiler that a successful matching consists of exactly $n$ capturing groups, where $n$ is the tuple's arity.
\begin{diff}
The |P| type is composed of |String| and |Option[String]| types, depending on the nullability of the correspond capturing group.
Our implementation enriches the results of Java's regex engine by wrapping nullable values into options, and packaging the overall result into a tuple of type P.
We perform this operation in the |transform| method, which is the runtime component of our library.
\end{diff}
As a result, our implementation never returns null values and removes the null-checking burden from the user.
